\subsection{Numerical Solutions}
    \subsubsection{Condition Number}
        Numerical solution is affected by round-off error. we define $\delta\w = \w -\Tilde{\w}$ and $\delta\y = \y -\Tilde{\y}$ where $\Tilde{\w},\Tilde{\y}$ are the numerical solutions to LSQ and $A\Tilde{\w} = \Tilde{\y}$.
        
        \textit{If $\|\delta\y\|$ is small is $\|\delta\w\|$ small as well?} $\Rightarrow$ No.
        
        Condition number:
        \begin{equation*}
            \colorboxed{red}{
                \kappa(A)=\|A\|\|A^{-1}\|
            } 
            \qquad \kappa(A)\in[0,\infty)
        \end{equation*}
        We call a problem \textit{well defined} if $\kappa(A)$ is not too large. In that case the computed solution will be close to the true solution.
        
        Interpretation: \textit{How close a Matrix is to being singular.}
        
        Orthogonal Matrices: $\kappa(A)=1$
        
        $\|A\|_2 = \sqrt{\rho(A^\top A)}$ where $\rho$ is the largest Eigenvalue
        
        $\kappa_2(A^\top A) = \kappa_2(A)^2 \Rightarrow$ bad for LSQ
        
    \subsubsection{QR decomposition}
        $Q\in\mathbb{R}^{N\times N}$ is orthogonal and $Q_1\in\mathbb{R}^{N\times M}$ is a matrix with orthogonal columns and $R_1\in\mathbb{R}^{M \times M}$ is upper triangle and invertible.
        \begin{equation*}
            \colorboxed{red}{
                A =\underbrace{\begin{bmatrix} Q_1 & Q_2 \end{bmatrix}}_Q \underbrace{\begin{bmatrix} R_1 \\ 0 \end{bmatrix}}_R = Q_1 R_1
            }\,
            \colorboxed{red}{
                \w = R_1^{-1}Q_1^\top \y
            }
        \end{equation*}
        $R_1$ is upper triangle $\rightarrow$ \textbf{no need to compute inverse}, just solve the Linear SoE 
        \begin{equation*}
            R_1\w=Q_1^\top\y,\quad 
            \textnormal{with: }\|R_1\|=\|R_1 Q_1\| = \|A\|
        \end{equation*}
        Condition of the matrices involved in the solution is the same as the condition of $A$
        
    \subsubsection{Singular Value Decomposition (SVD)}    
        The SVD of a Matrix $A\in\mathbb{R}^{N\times M}$ with $\textrm{rank}(A) = \rho$ decomposed $A$ as,
        \begin{equation*}
            A = \begin{bmatrix} U_r & U_n \end{bmatrix} \begin{bmatrix} S & 0 \\ 0 & 0 \end{bmatrix} \begin{bmatrix}V_r^\top \\ V_n^\top \end{bmatrix} = U\Sigma V^\top
        \end{equation*}
        $U\in\mathbb{R}^{N\times N}$ and $V\in\mathbb{R}^{M\times M}$ are orthogonal matrices. $\Sigma\in\mathbb{R}^{N\times M}$ is a diagonal matrix and
        $S = \textrm{diag}(\sigma_1,\dots,\sigma_\rho)$ where $\sigma_1 \geq \sigma_2 \geq \dots \sigma_\rho \geq 0$ with $\sigma_i$ being the \textit{singular values} of $A$.
        \begin{equation*}
            \Sigma^+ = \begin{bmatrix} S^{-1} & 0\\ 0 & 0 \end{bmatrix}
        \end{equation*}
        \textit{Moore-Penrose Pesudoinverse:}
        \begin{gather*}
            A^+ = (A^\top A)^{-1}A^\top,\quad
            \colorboxed{red}{
             A^+ = V\Sigma^+ U^\top
            }\\
            \colorboxed{red}{
                \w^\star = V\Sigma^+ U^\top \y
            }
        \end{gather*}
        $\Rightarrow\Sigma V^\top\w^\star = U^\top\y$ and $\kappa(\Sigma V^\top) = \kappa(A)$